\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
%\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ordepdev.me}{\Large Pedro Tavares}} & \href{mailto:pedrotavares.dev@gmail.com}{pedrotavares.dev@gmail.com}\\
  \href{http://ordepdev.me}{ordepdev.me} & +351932835322 \\
\end{tabular*}

\section{Interests}
  \centering{\textit{distributed systems, data-intensive applications, functional programming}} \\
 
\section{Relevant Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Talkdesk}{Porto, Portugal}
    {Software Engineer}{2018 - 2019}
    \resumeItemListStart
      \resumeItem{}{Teamed up with 2 highly skilled developers to ramp up a brand new data platform.}
      \resumeItem{}{Designed and developed a high throughput bridge from our core messaging system, RabbitMQ,
      to Apache Kafka to support all the required data processing, both in Elixir and Scala.}
      \resumeItem{}{Developed a stream processing layer on top of Kafka, providing a set of user-friendly DSLs
      to allow other teams apply their own business logic and deliver high quality read models to be queried by multiple systems afterwards.}
      \resumeItem{}{Delivered a highly scalable streaming API, written in Elixir, to make the connection between our data platform
      and real-time dashboards with multiple live subscribers. High quality standards were applied and we took care of problems like duplicates and backpressure.}
      \resumeItem{}{Performed as On-Call Engineer for API-Gateway and Talkdesk ID, the two entry points of Talkdesk. Created and tuned a few metrics, and
      wrote detailed and blameless post-mortems after the incidents, that were useful to make improvements in the affected systems.}
      \resumeItem{}{Evaluated candidates challenges and performed technical interviews with direct impact in the team. I was also responsible for coaching
      and mentoring newcomers in the team, by providing high value deep dive sessions around our core systems. Newcomers were ready to contribute after the
      first week on the job with pair and mob programming sessions. }
      \resumeItem{}{Started a weekly user group around computer science papers, mostly an in-house version of the Papers We Love meetup. It was great to see
      more people reading papers after each session.}
    \resumeItemListEnd

    \resumeSubheading
      {Farfetch}{Porto, Portugal}
      {Software Engineer}{2017 - 2018}
      \resumeItemListStart
        \resumeItem{}{Worked closely with the architecture team to design and implement
        a cross-company strategy to mask sensitive personal information backed by Apache Kafka and Cassandra.}
        \resumeItem{}{Extracted and scaled a legacy application to thousands of users
        through small endpoints that were exposed on a public API, designed with a CQRS architecture.}
        \resumeItem{}{Increased the test depth and coverage of a core and highly-available service that
        it is being used by the customer service department to perform direct sales.}
      \resumeItemListEnd

    \resumeSubheading
      {Jumia Services}{Porto, Portugal}
      {Software Engineer}{2016 - 2017}
      \resumeItemListStart
        \resumeItem{}{Designed, developed and tested highly concurrent and multi-timezone
        microservices using mainly Java, Spring Boot and Netflix OSS.}
        \resumeItem{}{Designed a solution to preserve the message processing ordering within
        multiple RabbitMQ consumers to improve the consistency of our microservices.}
        \resumeItem{}{Handled several concurrency issues in our data-intensive applications
        that dropped the error rate to nearly 0\%.}
        \resumeItem{}{Defined a new strategy to release multiple modules that performed 10
        times faster than the previous one.}
        \resumeItem{}{Designed and develop an end-to-end testing framework that dropped by
        almost 100\% the time needed to test a full new feature.}
        \resumeItem{}{Massively increased the testing coverage of our microservices through
        unit, integration, contract and end-to-end testing.}
      \resumeItemListEnd

    %\resumeSubheading
    %{Unicer}{Porto, Portugal}
    %{Software Engineer}{2015}
    %\resumeItemListStart
    %  \resumeItem{}{Responsible for building modules, mentoring team members, and releasing
    %  websites based on the Carlsberg Pegasus project: Super Bock, \'Agua das Pedras and
    %  Carslberg Where is the Party.}
    %\resumeItemListEnd

    %\resumeSubheading
    % {ORBCOM}{Porto, Portugal}
    % {Software Engineer}{2013 - 2014}
    %  \resumeItemListStart
    %    \resumeItem{}{Responsible for the ASP.NET MVC and Umbraco development as well as
    %    mentoring interns on both technologies with several in-house hands-on.}
    %    \resumeItem{}{Responsible for the development of e-commerce solutions using
    %    Umbraco and Merchello.}
    %  \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Engineering of the University of Porto}{Portugal}
      {Masters in Software Engineering}{2017 - (On hold)}
    \resumeSubheading
      {Polytechnic Institute Of C\'avado And Ave}{Portugal}
      {Bachelor in Health Informatics}{2009 - 2012}
  \resumeSubHeadingListEnd
  
%\section{Activities}
%  \resumeItemListStart
%      \resumeItem{}{Organizer of \href{https://www.meetup.com/Papers-We-Love-Porto/}{Papers We Love @ Porto}}
%      \resumeItem{}{I usually blog at at \href{http://ordepdev.me}{ordepdev.me} when I have something interesting to share}
%      \resumeItem{}{Spoke at \href{https://www.youtube.com/watch?v=AEtXHTGEweg}{Lambda Days}, \href{https://www.youtube.com/watch?v=MWLcRZUo9Mc}{ScaleConf Colombia}, \href{https://www.youtube.com/watch?v=SMhA2sEMtYQ}{Tech in Porto} and \href{https://www.youtube.com/watch?v=czyUG2Tp-3s}{Pixels Camp} and local meetups}
%      \resumeItem{}{Organized Hacktoberfest in Porto! 2017 \& 2018 Editions}      
%      \resumeItemListEnd

\end{document}
